Sparse Function-space Representation \\ of Neural Networks

### 2023-05-15 paper/main.tex
Sec. 1 WIP

%Need for adaptive learning methods + failures with current methods
In this paper, we demonstrate that any neural network can be represented in terms of the so-called `dual' parameters of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast}. Contrasting to previous work that use subsets \cite{immer2021scalable}, this parameterization allows squashing the contributions of {\em all} training data into a sparse representation. Crucially, the resulting GP now predicts in the same space as the originally trained neural network, a feature not present in previous approaches, while still avoiding the notorious cubic complexity of vanilla GPs. Given the dual parameter formulation, we can convert a full GP to a variational sparse version. Using the sparse GP we can then take advantage of the property of dual parameters that allows for fast conditioning recently shown in \cite{chang2022fantasizing}. Thus we are able to avoid retraining and condition new data in to our model. The resultant \our method can be used in any sequential decision-making scenario where retraining is not available.%and we show its effectiveness in a planning stage of a model based reinforcement algorithim.

\todo{a pragraph on how this can be used for improving CL and RL}

@@

We introduce a sparse representation of the neural network in the function space. 
%
{\em (i)}~principled uncertainty quantification.
{\em (ii)}~A compact representation for continual learning
{\em (iii)}~Fast updates for adaptive exploration.
%
We demonstrate points {\em(i)--(iii)} in the experiments.

>>>>

%Need for adaptive learning methods + failures with current methods
In this paper, we demonstrate that any neural network can be represented in terms of the so-called `dual' parameters of a GP~\cite{csato2002sparse, adam2021dual, chang2020fast}. Contrasting to previous work that use subsets \cite{immer2021scalable}, this parameterization allows squashing the contributions of {\em all} training data into a sparse representation. Crucially, the resulting GP now predicts in the same space as the originally trained neural network, a feature not present in previous approaches, while still avoiding the notorious cubic complexity of vanilla GPs. Given the dual parameter formulation, we establish a link between the neural network, the resulting full GP, and a sparse approximation of it akin to variational sparse GPs~\cite{titsias2009variational}. Using the sparse GP we can then take advantage of the property of dual parameters that allows for fast conditioning recently shown in \cite{chang2022fantasizing}. Thus we are able to avoid retraining and condition new data in to our model. The resultant \our method can be used in any sequential decision-making scenario where retraining is not available.
%\todo{a pragraph on how this can be used for improving CL and RL}

@@

The contributions of this paper are as follows.
%
{\em (i)}~We introduce \our, a new approah for sparse representation of the neural network in the function space.
{\em (ii)}~We show that, despite being sparse, the method gives a good   
A compact representation for continual learning
{\em (iii)}~Fast updates for adaptive exploration.
%
We provide extenive experiments for showcasing our approach and demonstrate importance and applicability across supervised, continual, and reinforcement learning to stimulate future use of the approach.
